analysis-pilot

### 2023-08-16 code/analysis-pilot.Rmd
passable timing data

# Veronica works on wrangling transcripts here

@@

games <- read_csv(here("data/games.csv"), col_types="ccc") %>% mutate(offset_sec=0)
#|> mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

@@

# write_csv(here(data, 'rounds7.19.csv'))
```

@@

wrangle_transcript <- function(game_num){
read_csv(here("data/clean_transcripts", str_c(game_num,".csv"))) |> 
  select(start, end, text, speaker) |> 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker))
}

@@

```{r, include=F, eval=F}
# a very derpy approach to aligning trial boundaries with transcripts

timing <- raw_data |> group_by(game) |> mutate(cum_time=cumsum(time), cum_sec=cum_time/1000+3*trialNum) |> select(trialNum, game, cum_sec) |> mutate(start=ifelse(trialNum==0, 0,lag(cum_sec)), end=cum_sec, trialNumStart=trialNum, trialNumEnd=trialNum, speaker=NA, text=NA) |> select(-cum_sec, -trialNum)

timed_transcripts <- transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -time, -gameId) |> 
  rename(game=gameConfig) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  bind_rows(timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(start>0)

# turns out this isn't good enough for timing, let's try stages instead!

@@

stage_timing <- stages |> left_join(gameStarts) |> mutate(rel_time=startTimeAt-first) |> mutate(rel_time=lubridate::as.period(rel_time) |> lubridate::period_to_seconds()) |> filter(index%%2==0) |> mutate(trialNum=index/2) |> select(gameId, trialNum, start=rel_time, end=rel_time) |> left_join(games) |> mutate(trialNumStart=trialNum, trialNumEnd=lag(trialNum)) |> ungroup() |> select(game=gameConfig, trialNumStart, trialNumEnd, start, end) |> filter(!is.na(game)) |> filter(!is.na(start)) |> filter(!is.na(end))
```

```{r}
timed_transcripts <-  transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -time, -gameId) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  rename(game=gameConfig) |> 
  bind_rows(stage_timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(!is.na(text)) |> 
  write_csv(here("data/timed_transcript.csv"))
```

>>>>

# Data prep

@@

games <- read_csv(here("data/games.csv"), col_types="ccc")|> mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

@@

@@

wrangle_transcript <- function(game_num){
read_csv(here("data/clean_transcripts", str_c(game_num,".csv")), show_col_types=F) |> 
  select(start, end, text, speaker) |> 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker))
}

@@

@@

stage_timing <- stages |> left_join(gameStarts) |>
  mutate(rel_time=startTimeAt-first) |> 
  mutate(rel_time=lubridate::as.period(rel_time) |> lubridate::period_to_seconds()) |> 
   mutate(trialNum=index/2,
          start=rel_time,
          end=lead(rel_time)) |> 
  select(gameId, trialNum,start, end) |>  left_join(games) |>  ungroup() |> 
  mutate(trialNumStart=trialNum, trialNumEnd=trialNum) |> 
  select(game=gameConfig, trialNumStart, trialNumEnd, start, end) |> filter(!is.na(game)) |> filter(!is.na(start)) |> filter(!is.na(end))
```

```{r}
timed_transcripts <-  transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -gameId) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  rename(game=gameConfig) |> 
  bind_rows(stage_timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(!is.na(text)) |> 
  write_csv(here("data/timed_transcript.csv"))
```

```{r}
# how many trial mismatches are there?
timed_transcripts |> filter(end>0) |> filter(!is.na(trialNumEnd)) |> #it's in the game region, not rules or post game
 mutate(mismatch=trialNumEnd-trialNumStart) |> 
  group_by(mismatch) |> 
  tally()

#so like a third mismatch, and only a couple off by more than 1
```
